Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-13 papers/B1555_EdgeOn/B1555_letter.tex
update point_source figure
large change in Intro, small change in Modeling. New references not updated yet

\section{Introduction}
Flux ratio anomaly in gravitational lensed systems has been seen as a promising method to probe substructures within halos.
Base on the concordant cold dark matter cosmology, simulations show more substructures than up-to-date observation searches.
This ``missing satellite'' problem arose interesting discrepancy between theoretical and observational understanding on structure
formation. \\
One possible explanation to this discrepancy is the difficulties of searching low-mass satellites(typical mass range?). Recent research shows using gravitational lensing effects from substructures can lower the detectable mass limit (mass range). More satellite galaxy candidates would be discovered from flux ratio anomaly in strong lensed galaxy systems, which may give us new insights to structures within dark matter halo. \\
On the other hand, simulations haven't reach a concise conclusion on the cause of flux ratio anomaly. Substructures may not be the only reason for flux ratio anomalies in merging double or triple images. Dust extinction, micro lensing from stars, and structures belongs to lens galaxy can also contribute to flux ratio anomaly. These factors would affect the estimation of substructure mass and even give false signal when searching possible satellite candidates.\\
In the latest SHARP observation, we aimed on several strong lensed systems with flux ratio anomaly discovered. Clear edge-on disk is found in the infrared images of (systems). To probe the causes of flux ratio anomaly, we model one system, B1555+375, with a center bulge and an edge-on disk. (B1555 radio observation details in intro?) In this paper, we present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The full best-fit parameters are shown in Table 1.

@@

\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets measured from component A in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}

>>>>

\section{Introduction}
To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group. Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way. Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness due to perturbations in gravitational potential. Little perturbation from substructures (mass range?) is sufficent to bring flux ratio anomalies in strong lensed systems. In the observational view, radio observation is the best way to probe these flux ratio anomalous systems because it doesn't have severe extinction issue like in optical or infrared band. Also, most radio lensed images are point sources which are easier to model. \\
On the other hand, results from numerical simulation haven't reach a concise conclusion on the cause of flux ratio anomaly. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lesing systems. We obtain high-resoltion images from Keck adaptive optics(AO) Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The full best-fit parameters are shown in Table 1. We also try on another model with two SIE mass profiles. This model will be used in the following up study with Simona...

@@

\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}
